---
title: "Introducción a distribuciones de abundancia de especies"
date: "2026-09-21" 
author:
  - name: Paulo Inácio Prado
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(eval = FALSE)
source("funciones.R")
# clipboard
htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "Copy code <i class=\"fa fa-clipboard\"></i>",
    success_text = "Copied! <i class=\"fa fa-check\" style=\"color: #90BE6D\"></i>",
    error_text = "Not copied 😕 <i class=\"fa fa-times-circle\" style=\"color: #F94144\"></i>"
  ),
  rmarkdown::html_dependency_font_awesome()
  )

```

# Slides

```{r slides, echo=FALSE, eval=TRUE}
xaringanExtra::embed_xaringan("01_introduccion/slides.html")
```

# Tutoriales

<details>
<summary><b>1. Gráficos</b></summary>

# La línea de corte de Preston

```{r capitulo-preston, echo = FALSE, results = "asis", eval = TRUE}
cat(incluir_capitulo("01_introduccion/linea_corte_preston.Rmd", eval = FALSE), sep = "\n")
```

</details>

# Referencias

Fisher, R.A., Corbet, A.S. and Williams, C.B. (1943) The relation between the number of species and the number of individuals in a random sample of an animal population. *Journal of Animal Ecology*, 12: 42–58.

Green, J. and Plotkin, J.B. (2007) A statistical theory for sampling species abundances. *Ecology Letters*, 10: 1037–1045.

Pielou, E.C. (1977) *Mathematical Ecology*. New York: John Wiley and Sons.

Preston, F.W. (1948) The commonness, and rarity, of species. *Ecology*, 29(3): 254–283.

